The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-25 background.tex
add picture
start to structure the paper
tell the philosophy
rearrange the paper structure

\subsection{List of basic terminology} % (fold)
\label{sub:list_of_basic_terminology}
here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities.
	\item 
\end{itemize}
% subsection list_of_basic_terminology (end)

@@

\subsubsection{Cloud manufacturing architecture}
\label{subs:cloud manufacturing architecture}
Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
\caption{Cloud manufacturing architecture with main flows}
\label{fig:structure}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.7\textwidth]{usertype.pdf}
	\caption{Simple explanation of user type}
	\label{fig:usertype}
\end{figure}

\begin{table}[htbp]
	\caption{Simple explanation of user type}
	\label{tab:usertype}
	\centering

	\begin{tabularx}{\textwidth}{llX}
	\toprule
	\textbf{Type} & \textbf{Name} &  \textbf{Concise Description}\\
	\midrule
	I			& Pure demander &  Submit manufacturing tasks and make evaluation of provider.\\
	II 			& Complex user 	&  Usually a pure provider submit part of its task, it becomes the complex user and changes the operation model of the user.\\
	III 		& Pure provider &  Provide manufacturing services and makes evaluation demander.\\
	\bottomrule
	\end{tabularx}
\end{table}
% Before the emendation of the roles, some related standard name should be taken:

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementary illustration for \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

@@

\begin{table}[tb]
	\caption{Core modules in operation model of platform}
	\label{tab:core_module_in_platform}
	\centering

	\begin{tabularx}{\textwidth}{llX}
	\toprule

@@

\begin{figure}[htbp]
\centering
\subfloat[Pure demander]{\includegraphics[width=0.75\textwidth]{demander_main_process}\label{fig:demanderprocess}}\\
\subfloat[Complex user]{\includegraphics[width=0.75\textwidth]{complex_main_process}\label{fig:complexprocess}}\\
\subfloat[Pure Provider]{\includegraphics[width=0.75\textwidth]{provider_main_process}\label{fig:providerprocess}}
\caption{Main operational processes}
\label{fig:useroperation}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Users' changes}
	\label{tab:userchange}
	\centering
	\begin{tabularx}{\textwidth}{llX}
	\toprule
	\textbf{Change} & \multicolumn{2}{l}{\textbf{Appearance with concise description}}\\
	\midrule
	\multirow{3}*{Type}			& Complex user $\to$ Pure demander: & User stop provide its resource\\
								& Complex user $\to$ Pure provider: & User shrink service area that only contains its own service \\
								& Pure provider $\to$ Complex user: & User extend service area that starts to contain service from others' \\
	\midrule
	\multirow{4}*{Status} 		& Pure demander enter ecosystem: &	One pure demander starts to publish orders\\
								& Pure demander exit ecosystem: & One pure demander be banned to publish orders\\
								& Pure provider enter ecosystem: & Administrator introduces one provider into the ecosystem\\
								& Pure provider exit ecosystem: & Administrator eliminates one provider form the ecosystem\\
	\midrule
	\multirow{2}*{Niche width} 	& Widen: & One provider extends its service area\\
								& Narrow down:  & One provider shrinks its service area\\
	\bottomrule
	\end{tabularx}
\end{table}

@@

\begin{table}[htbp]
 	\caption{Macroscopic evolution}
 	\label{tab:macroevolution}
 	\centering
 	\begin{tabularx}{\textwidth}{llX}
 	\toprule
 	\textbf{column 1} & \multicolumn{2}{l}{\textbf{Appearance with concise description}} \\
 	\midrule
 	Amount & & \\
 	Diversity & & \\
 	Service cycle rate & & \\
 	\bottomrule
 	\end{tabularx}
 \end{table}

>>>>

\subsection{List of basic terminology} % (fold)
\label{sub:list_of_basic_terminology}
here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities. the proportion of the capacities.
	\item 
\end{itemize}
% subsection list_of_basic_terminology (end)

@@

\subsubsection{Cloud manufacturing architecture}
\label{subs:cloud manufacturing architecture}
Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
\begin{figure}[htbp]
\centering
\includegraphics[scale = .3, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
\caption{Cloud manufacturing architecture with main flows}
\label{fig:structure}
\end{figure}

@@

% \begin{figure}[htbp]
% 	\centering
% 	\includegraphics[width=.7\textwidth]{usertype.pdf}
% 	\caption{Simple explanation of user type}
% 	\label{fig:usertype}
% \end{figure}

% \begin{table}[htbp]
% 	\caption{Simple explanation of user type}
% 	\label{tab:usertype}
% 	\centering
% 	\tiny
% 	\begin{tabularx}{\textwidth}{llX}
% 	\toprule
% 	\textbf{Type} & \textbf{Name} &  \textbf{Concise Description}\\
% 	\midrule
% 	I			& Pure demander &  Submit manufacturing tasks and make evaluation of provider.\\
% 	II 			& Complex user 	&  Usually a pure provider submit part of its task, it becomes the complex user and changes the operation model of the user.\\
% 	III 		& Pure provider &  Provide manufacturing services and makes evaluation demander.\\
% 	\bottomrule
% 	\end{tabularx}
% \end{table}
% Before the emendation of the roles, some related standard name should be taken:

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale = .3, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementary illustration for \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

@@

\begin{table}[tb]
	\caption{Core modules in operation model of platform}
	\label{tab:core_module_in_platform}
	\centering
	\scriptsize
	\begin{tabularx}{\textwidth}{llX}
	\toprule

@@

% \begin{figure}[htbp]
% \centering
% \subfloat[Pure demander]{\includegraphics[width=0.75\textwidth]{demander_main_process}\label{fig:demanderprocess}}\\
% \subfloat[Complex user]{\includegraphics[width=0.75\textwidth]{complex_main_process}\label{fig:complexprocess}}\\
% \subfloat[Pure Provider]{\includegraphics[width=0.75\textwidth]{provider_main_process}\label{fig:providerprocess}}
% \caption{Main operational processes}
% \label{fig:useroperation}
% \end{figure}

@@

% \begin{table}[htbp]
% 	\caption{Users' changes}
% 	\label{tab:userchange}
% 	\centering
% 	\scriptsize
% 	\begin{tabularx}{\textwidth}{llX}
% 	\toprule
% 	\textbf{Change} & \multicolumn{2}{l}{\textbf{Appearance with concise description}}\\
% 	\midrule
% 	\multirow{3}*{Type}			& Complex user $\to$ Pure demander: & User stop provide its resource\\
% 								& Complex user $\to$ Pure provider: & User shrink service area that only contains its own service \\
% 								& Pure provider $\to$ Complex user: & User extend service area that starts to contain service from others' \\
% 	\midrule
% 	\multirow{4}*{Status} 		& Pure demander enter ecosystem: &	One pure demander starts to publish orders\\
% 								& Pure demander exit ecosystem: & One pure demander be banned to publish orders\\
% 								& Pure provider enter ecosystem: & Administrator introduces one provider into the ecosystem\\
% 								& Pure provider exit ecosystem: & Administrator eliminates one provider form the ecosystem\\
% 	\midrule
% 	\multirow{2}*{Niche width} 	& Widen: & One provider extends its service area\\
% 								& Narrow down:  & One provider shrinks its service area\\
% 	\bottomrule
% 	\end{tabularx}
% \end{table}

@@

\begin{table}[htbp]
 	\caption{Macroscopic evolution}
 	\label{tab:macroevolution}
 	\centering
 	\scriptsize
 	\begin{tabularx}{\textwidth}{llX}
 	\toprule
 	\textbf{column 1} & \multicolumn{2}{l}{\textbf{Appearance with concise description}} \\
 	\midrule
 	Amount & & \\
 	Diversity & & \\
 	Service cycle rate & & \\
 	\bottomrule
 	\end{tabularx}
 \end{table}

### 2016-08-25 figures/scheduleChart.tex
add nomecalture
rearrange the paper structure

\fill[blue!20!,yshift=18cm] (5cm,4cm) rectangle (7cm,5cm);
\draw[yshift=18cm] (2cm,0) rectangle (5cm,3cm) (5cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm,1.6cm) node{$t_3$} (6.5cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$};
\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm);
\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$};
\draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$};
\draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (2cm,0) rectangle (5cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

>>>>

\fill[blue!20!,yshift=18cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=18cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
\draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}
